[dcpo_demsupport]

### 2020-08-07 paper/dcpo_demsupport.Rmd
resolve conflicts per https://github.com/fsolt/dcpo_dem_mood/issues/10#issuecomment-670695515
per #9

```{r dcpo_input_raw}
dcpo_input_raw <- DCPOtools::dcpo_setup(vars = read_csv("data-raw/mood_dem.csv",
                                                          col_types = "cccccc"),
                                          file = "data/dcpo_input_raw.csv")
```

```{r dcpo_input}
dcpo_input_raw1 <- read_csv("data/dcpo_input_raw.csv", col_types = "cdcddcd") %>% 
  filter(!(str_detect(survey, "army_wvs") & # WVS obs identified as problematic by Claassen 
                 ((country=="Albania" & year==1998) |
                      (country=="Indonesia" & (year==2001 | year==2006)) |
                      (country=="Iran" & year==2000) |
                      (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
                      (country=="Vietnam" & year==2001)) |
                 (str_detect(item, "strong_wvs") &
                      ((country=="Egypt" & year==2012) |
                           (country=="Iran" & (year==2000 | year==2007)) | # 2005 in Claassen
                           (country=="India") |
                           (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
                           (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
                           (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
                           (country=="Vietnam" & year==2001))) |
                 (country %in% c("Puerto Rico", "Northern Ireland", 
                                 "SrpSka Republic", "Hong Kong SAR China")))) %>%
  with_min_yrs(2)

@@

```{r compare_n}
if (!file.exists("data/supdem raw survey marginals.tab")) {
  dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>% 
    read_csv(col_types = "cdcddcdc") %>% 
    write_csv("data/supdem raw survey marginals.tab")
}

@@

```{r country_years}
path_df <-
  list.files(
    "../data",
    pattern = ".*_theta.rda",
    recursive = TRUE,
    full.names = TRUE
  ) %>%
  .[str_which(., "claassen")]

@@

```{r dcpo-uncertainty, cache=TRUE}
# Preload function ----
vcovBK_se <- function(x) {
  plm::vcovBK(x, cluster = "time") %>% 
    diag() %>% 
    sqrt()
}

# Data input ----

load(here::here("data", "dcpo_theta.rda"))

df_controls <- read_csv(here::here("data", "control_variables.csv"),
                        col_types = cols(.default = col_double(),
                                         country = col_character(),
                                         country_name = col_character(),
                                         ISO = col_character(),
                                         Region_UN = col_character())) %>% 
  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
         country = countrycode::countrycode(country0, "country.name", "country.name"))

@@

df_dcpo <- purrr::map(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>% 
    reformat_dcpo_output("theta") %>% 
    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
              by = c("year", "country")) %>% 
    left_join(df_controls, by = c("country", "year")) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

result_dcpo_1k <- map(df_dcpo, function(aDataset) {
  plm::plm(Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + plm::lag(theta, 1) +
             plm::lag(sigma, 1) + plm::lag(lg_imp_mdpgdp, 1) +
             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1),
    model = "pooling",
    data = aDataset)
})

@@

df_result_dcpo <- summary(mitools::MIcombine(results = result_betas_dcpo_1k, variance = result_vars_dcpo_1k)) %>% rownames_to_column(var = "term") %>% 
  rename(conf.low = `(lower`,
         conf.high = `upper)`, 
         estimate = results) %>% 
  filter(!str_detect(term, "(Intercept)"))

>>>>

```{r dcpo_input_raw, eval = FALSE}
dcpo_input_raw <- DCPOtools::dcpo_setup(vars = read_csv("data-raw/mood_dem.csv",
                                                          col_types = "cccccc"),
                                          file = "data/dcpo_input_raw.csv")
```

```{r dcpo_input, eval = FALSE}
dcpo_input_raw1 <- read_csv("data/dcpo_input_raw.csv", col_types = "cdcddcd") %>% 
  filter(!(str_detect(survey, "army_wvs") & # WVS obs identified as problematic by Claassen 
                 ((country=="Albania" & year==1998) |
                      (country=="Indonesia" & (year==2001 | year==2006)) |
                      (country=="Iran" & year==2000) |
                      (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
                      (country=="Vietnam" & year==2001)) |
                 (str_detect(item, "strong_wvs") &
                      ((country=="Egypt" & year==2012) |
                           (country=="Iran" & (year==2000 | year==2007)) | # 2005 in Claassen
                           (country=="India") |
                           (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
                           (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
                           (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
                           (country=="Vietnam" & year==2001))) |
                 (country %in% c("Puerto Rico", "Northern Ireland", 
                                 "SrpSka Republic", "Hong Kong SAR China")))) %>%
  with_min_yrs(2)

@@

```{r compare_n, eval = FALSE}
if (!file.exists("data/supdem raw survey marginals.tab")) {
  dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>% 
    read_csv(col_types = "cdcddcdc") %>% 
    write_csv("data/supdem raw survey marginals.tab")
}

@@

```{r country-years, eval=FALSE}
path_df <-
  list.files(
    "../data",
    pattern = ".*_theta.rda",
    recursive = TRUE,
    full.names = TRUE
  ) %>%
  .[str_which(., "claassen")]

@@

```{r claassen-replication}
# Data input ----

supdem <- read.csv("../data/Support_democracy_ajps.csv")
v_dem <- read.csv("../data/vdem15.csv")

sd.plm <- pdata.frame(supdem, index = c("Country", "Year"))

# Pooled model -----

## Beck-Katz panel-corrected standard errors
vcovBK_se <- function(x) {
  plm::vcovBK(x, cluster = "time") %>% 
    diag() %>% 
    sqrt()
}

# regime = ifelse(sd2$Regime_VD > 1, 1, 0)

ls_mod <-
  paste0(
    "Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + ",
    c(
      "plm::lag(SupDem_trim, 1)",
      "plm::lag(SupDem_Democ, 1) + plm::lag(SupDem_Autoc, 1)"
    ),
    "+ plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)"
  )

result_cls <- map(ls_mod, function(mod){
  result <- plm(ls_mod, model = "pooling", data = sd.plm)
  df_result <- tidy(result) %>%
    mutate(std.error = vcovBK_se(result))
})

# GMM ----

## Windmeijer corrected standard errors
vcovHC_se <- function(x) {
  plm::vcovHC(x, cluster = "time") %>% 
    diag() %>% 
    sqrt()
}

ls_mod <- 
  paste0(
    "Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + ",
    c(
      "plm::lag(SupDem_trim, 1)",
      "plm::lag(SupDem_Democ, 1) + plm::lag(SupDem_Autoc, 1)"
    ),
    "+ plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)",
    " | plm::lag(Libdem_VD, 3:5)"
  )

result_cls[3:4] <- map(ls_mod, function(mod){
  result <- pgmm(as.formula(ls_mod), effect="individual", model="onestep", transformation="ld", indexes=c("Country", "Year"), data = sd.plm)
  df_result <- coef(result) %>% 
    tibble::enframe(name = "term", value = "estimate") %>% 
    mutate(std.error = vcovHC_se(result))
})

```{r dcpo-uncertainty, cache=TRUE}

# Data input ----
load(here::here("data", "dcpo_input.rda"))
load(here::here("data", "dcpo_sigma.rda"))
load(here::here("data", "dcpo_theta.rda"))

df_controls <- read_csv(here::here("data", "control_variables.csv"),
                        col_types = cols(.default = col_double(),
                                         country = col_character(),
                                         country_name = col_character(),
                                         ISO = col_character(),
                                         Region_UN = col_character())) %>% 
  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
         country = countrycode::countrycode(country0, "country.name", "country.name"),
         regime = Vdem_libdem > 1)

@@

df_dcpo <- purrr::map(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>% 
    reformat_dcpo_output("theta") %>% 
    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
              by = c("year", "country")) %>%
    left_join(df_controls, by = c("country", "year")) %>% 
    mutate(theta_dem = theta * regime,
           theta_aut = theta * (1 - regime)) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

estimate_dcpo_pooled <- function(aModel) {
  result_dcpo_1k <- map(df_dcpo, function(aDataset) {
    plm::plm(aModel,
             model = "pooling",
             data = aDataset)
  })

@@

  df_result_dcpo <-
    summary(
      mitools::MIcombine(results = result_betas_dcpo_1k, variance = result_vars_dcpo_1k)
    ) %>% rownames_to_column(var = "term") %>%
    rename(conf.low = `(lower`,
           conf.high = `upper)`,
           estimate = results) %>%
    filter(!str_detect(term, "(Intercept)"))
}

mod_ls <- paste0(
  "Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + ", 
  c("plm::lag(theta, 1)", 
    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
  " + plm::lag(lg_imp_mdpgdp, 1) +
             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)"
)

df_result_dcpo <- map(mod_ls, estimate_dcpo_pooled)

estimate_dcpo_gmm <- function(aModel) {
  result_dcpo_1k <- map(df_dcpo, function(aDataset) {
    pgmm(as.formula(aModel), effect="individual", model="onestep", transformation="ld", indexes=c("Country", "Year"), data = aDataset)
  })

  result_betas_dcpo_1k <-
    mitools::MIextract(result_dcpo_1k, fun = coef)
  result_vars_dcpo_1k <-
    mitools::MIextract(result_dcpo_1k, fun = vcovHC_se)

  df_result_dcpo <-
    summary(
      mitools::MIcombine(results = result_betas_dcpo_1k, variance = result_vars_dcpo_1k)
    ) %>% rownames_to_column(var = "term") %>%
    rename(conf.low = `(lower`,
           conf.high = `upper)`,
           estimate = results) %>%
    filter(!str_detect(term, "(Intercept)"))
}

mod_ls <- paste0(
  "Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + ", 
  c("plm::lag(theta, 1)", 
    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
  " + plm::lag(lg_imp_mdpgdp, 1) +
             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)",
    " | plm::lag(Vdem_libdem, 3:5)"
)

df_result_dcpo[3:4] <- map(mod_ls, estimate_dcpo_gmm)
